\Large \bf On semidefinite-representable sets over valuation fields

### 2025-05-23 article/paper_padic_spec.tex
commit by Simone

Contrary to the LP case, the complexity status of SDP is widely open. In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{1}{R})$, where $R$ is an {\it a priori} upper bound on the norm of a solution, cf. \cite[Sec.1.9]{deKlerk}. In exact arithmetic, the complexity status of SDP is essentially open but complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by exploiting the determinantal structure of the constraints \cite{henrion2016exact}.

>>>>

Contrary to the LP case, the complexity status of SDP is widely open. In a fixed-precision model of computation, SDP is solvable in polynomial time in the input size (matrix size, number of variables, bit size of the coefficients), in $\log(\frac{1}{\varepsilon})$ (where $\varepsilon$ is the precision) and $\log(\frac{R}{r})$, where $r,R$ are radii of balls respectively included in and containing the feasible set, cf. \cite{grotschel1981ellipsoid} or \cite[Thm.1.1]{de2016turing} (see also \cite[Sec.1.9]{deKlerk}). In exact arithmetic, complexity bounds are known based either on general quantifier elimination \cite{ramana1997exact,porkolab1997complexity} or by means of a dedicated application of the critical point method exploiting the determinantal structure of the constraints \cite{henrion2016exact,NALDI2018206}.
